Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-11 inc/extension/external_forces/practical.tex
citations are now preceeded by non-breaking space (~)

The mathematical formalism developed in Section \ref{sec:external_forces} is only an abstract mechanism for including external forces.
To model electron pulses traveling through realistic electron microcope columns, these abstract mechanisms must be developed further to properly describe each specific electron-optical element.
In the following section, I demonstrate concrete applications of the extended AG model, including magnetic lenses, radio-frequency (RF) cavities (useful for both pulse compression \cite{oudheusden_electron_2007} and acceleration %TODO refs
) and DC acceleration regions (i.e. electron gun dynamics).

@@

The full description of the motion of an electron (in cylindrical coordinates $r, \theta, z$) in an azimuthally symmetric magnetic field ($\vec{B} = B_r \hat{r} + B_z \hat{z}$) is easily derived \cite{el-kareh_electron_1970},
\begin{subequations} \label{eq:lens_eq_of_motion}
\begin{gather}
  m \ddot{r} = -e B_z r \dot{\theta} + m r \dot{\theta}^2                 \\
  \frac{d}{dt} ( m r^2 \dot{\theta} ) = e r \dot{r} B_z - e r B_r \dot{z} \\
  m \ddot{z} = e B_r r \dot{\theta} \,\text{,}
\end{gather}
\end{subequations}
where each dot denotes a time derivative.
Attempting to further seperate these equations quickly highlights the tightly coupled nature of the motion of the electron in this system.
Compounding the problem, the full description of the off-axis field of a real (non-infinite) air-core solenoid is also surprisingly complicated.
Montgomery and Terrell \cite{montgomery_some_1961} provide a full treatment for many lens configurations, including a tractable treatment for a single current loop of radius $a$, again in cylindrical coordinates, 
\begin{subequations} \label{eq:field_of_loop}
\begin{gather}
  \frac{B_z}{\mu} = H_z = \frac{2I}{\sqrt{Q}} \left(   F(k) + \frac{ a^2 - r^2 - z^2 }{ (1-k^2) Q } E(k) \right) \\
  \frac{B_r}{\mu} = H_r = \frac{2I}{\sqrt{Q}} \left( - F(k) + \frac{ a^2 + r^2 + z^2 }{ (1-k^2) Q } E(k) \right) \\
  Q \equiv (a+r)^2 + z^2 \\
  k \equiv \sqrt{ 4 a r / Q } \,\text{,}
\end{gather}
\end{subequations}
where $\mu$ is the local magnetic permability, $H$ is the auxiliary field, and $F(k)$ and $E(k)$ are the complete elliptic integrals of the first and second kind respectively.
In the vacuum, $\mu$ is simply the usual free space permeability $\mu_0$; in Section \ref{sec:mag_lens}, we will see how this permeability can be used to improve the performance of magnetic lenses.
An even more accurate solenoid can be modeled by appropriately summing the fields of many such loops.

@@

In the longitudinal ($ z $) direction, a resonant radio-frequency (RF) cavity can be used in a UEM column or UED experiment \cite{oudheusden_electron_2007,fill_sub-fs_2006} to act as a pulse compression or `temporal focusing' element.
The model of the RF cavity is different from the magnetic lens in two distinct ways.
First, the RF cavity contains several different fields and thus contributes several different linear force terms to the overall equation set.
Second, though there are more terms, their magnitudes are easily connected to the physical characteristics of the cavity.

Although there are many possible resonant cavity structures \cite{oudheusden_electron_2007,humphries_principles_1986}, for simplicity, this analysis will consider only the evacuated cylindrical (or `pillbox') $\text{TM}_{010}$ cavity for which the electrons propagate down the axis \cite{fill_sub-fs_2006,humphries_principles_1986}.
The known mathematical forms of the electric and magnetic components of this resonant mode together with a super-Gaussian envelope function (\ref{eq:reg_of_influence}) allow the three main effects of a pill-box RF cavity element on the electron pulse to be described within the approximation of the linear force extension to the AG model: the primary action of the pulse compression (or acceleration and expansion dependent upon the relative RF phase), and the transverse lens effects due to the magnetic component of the $\text{TM}_{010}$ resonance and the electric RF cavity fringe fields at its entrance and exit apertures \cite{kim_rf_1989}.

@@

The two main effects contributing to the transverse lens of a $\text{TM}_{010}$-mode RF cavity, its magnetic field component and electric fringe field aperture effects, may also be included within the linear force approximation.
The azimuthal magnetic component of the resonant mode oscillates 90$^{\circ}$ out of phase with the electric component and with a $\operatorname{ J_{1} }$ Bessel radial form; i.e., $ \operatorname{ J_{1} }( k r / a ) \sim k r / a $ for small $r$.
Symmetry and Gauss' Law dictate that in the vicinity of the axial center of the entrance and exit apertures of the RF cavity there exists a radial component of the oscillating electric field determined by $ E_{r} = -\left ( r / 2 \right ) \left ( \partial E_{z} / \partial z \right )_{r=0} $ \cite{kim_rf_1989}, where the form of the axial electric field for $\text{TM}_{010}$ oscillation (\ref{eq:RF_Efield}) implies that, in the context of this analysis, its axial gradient is solely dependent upon the envelope function for the RF cavity (\ref{eq:reg_of_influence}).
In practice, of course, the exact form of $E_{r}(z)$ is strongly tied to the size and shape of the RF cavity apertures (see for example $1 \frac{1}{2}$-cell RF photo-gun designs \cite{mcdonald_design_1988}). 
For the case of an evacuated cavity, these two contributions result in a net force,
\begin{equation} \label{eq:RF_Force_r}
  \boldsymbol{F}_{ r , RF } = e E_{0} \left [ 
    \frac{ v_{\smallzero} \Omega }{c^{2}} \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) + \frac{2 n}{d} \left ( \frac{z^{\prime} - z^{\prime}_{RF}}{d / 2} \right )^{2 n - 1} \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right )
   \right ] r \hat{\operatorname{ \boldsymbol{r} }} \text{.}
\end{equation}
In obtaining \ref{eq:RF_Force_r}, which is also of the form for use in \ref{eq:linear_force}, we have again used an arbitrary super-Gaussian of order $n$ as a region of influence envelope (see \ref{eq:reg_of_influence}) with $L_{RF} \equiv d$, the RF cavity length.
As will be seen in Section \ref{sec:rf_cav_charge}, under the pulse compression conditions ($\phi = 0$ when the pulse is at $z^{\prime} = 0$), both effects are defocusing for the electron pulse and the magnetic contribution is generally smaller than the transverse lenses associated with the RF cavity apertures when $ d = \pi v_{\smallzero} / \Omega $ \cite{kim_rf_1989}, even though its magnitude is maximized for $\phi = 0$.
Other effects, such as magnetic fringe field aperture effects, could also be included, but are significantly weaker.

>>>>

The mathematical formalism developed in Section \ref{sec:external_forces} is only an abstract mechanism for including external forces.
To model electron pulses traveling through realistic electron microcope columns, these abstract mechanisms must be developed further to properly describe each specific electron-optical element.
In the following section, I demonstrate concrete applications of the extended AG model, including magnetic lenses, radio-frequency (RF) cavities (useful for both pulse compression~\cite{oudheusden_electron_2007} and acceleration %TODO refs
) and DC acceleration regions (i.e. electron gun dynamics).

@@

The full description of the motion of an electron (in cylindrical coordinates $r, \theta, z$) in an azimuthally symmetric magnetic field ($\vec{B} = B_r \hat{r} + B_z \hat{z}$) is easily derived~\cite{el-kareh_electron_1970},
\begin{subequations} \label{eq:lens_eq_of_motion}
\begin{gather}
  m \ddot{r} = -e B_z r \dot{\theta} + m r \dot{\theta}^2                 \\
  \frac{d}{dt} ( m r^2 \dot{\theta} ) = e r \dot{r} B_z - e r B_r \dot{z} \\
  m \ddot{z} = e B_r r \dot{\theta} \,\text{,}
\end{gather}
\end{subequations}
where each dot denotes a time derivative.
Attempting to further seperate these equations quickly highlights the tightly coupled nature of the motion of the electron in this system.
Compounding the problem, the full description of the off-axis field of a real (non-infinite) air-core solenoid is also surprisingly complicated.
Montgomery and Terrell~\cite{montgomery_some_1961} provide a full treatment for many lens configurations, including a tractable treatment for a single current loop of radius $a$, again in cylindrical coordinates, 
\begin{subequations} \label{eq:field_of_loop}
\begin{gather}
  \frac{B_z}{\mu} = H_z = \frac{2I}{\sqrt{Q}} \left(   F(k) + \frac{ a^2 - r^2 - z^2 }{ (1-k^2) Q } E(k) \right) \\
  \frac{B_r}{\mu} = H_r = \frac{2I}{\sqrt{Q}} \left( - F(k) + \frac{ a^2 + r^2 + z^2 }{ (1-k^2) Q } E(k) \right) \\
  Q \equiv (a+r)^2 + z^2 \\
  k \equiv \sqrt{ 4 a r / Q } \,\text{,}
\end{gather}
\end{subequations}
where $\mu$ is the local magnetic permability, $H$ is the auxiliary field, and $F(k)$ and $E(k)$ are the complete elliptic integrals of the first and second kind respectively.
In the vacuum, $\mu$ is simply the usual free space permeability $\mu_0$; in Section \ref{sec:mag_lens}, we will see how this permeability can be used to improve the performance of magnetic lenses.
An even more accurate solenoid can be modeled by appropriately summing the fields of many such loops.

@@

In the longitudinal ($ z $) direction, a resonant radio-frequency (RF) cavity can be used in a UEM column or UED experiment~\cite{oudheusden_electron_2007,fill_sub-fs_2006} to act as a pulse compression or `temporal focusing' element.
The model of the RF cavity is different from the magnetic lens in two distinct ways.
First, the RF cavity contains several different fields and thus contributes several different linear force terms to the overall equation set.
Second, though there are more terms, their magnitudes are easily connected to the physical characteristics of the cavity.

Although there are many possible resonant cavity structures~\cite{oudheusden_electron_2007,humphries_principles_1986}, for simplicity, this analysis will consider only the evacuated cylindrical (or `pillbox') $\text{TM}_{010}$ cavity for which the electrons propagate down the axis~\cite{fill_sub-fs_2006,humphries_principles_1986}.
The known mathematical forms of the electric and magnetic components of this resonant mode together with a super-Gaussian envelope function (\ref{eq:reg_of_influence}) allow the three main effects of a pill-box RF cavity element on the electron pulse to be described within the approximation of the linear force extension to the AG model: the primary action of the pulse compression (or acceleration and expansion dependent upon the relative RF phase), and the transverse lens effects due to the magnetic component of the $\text{TM}_{010}$ resonance and the electric RF cavity fringe fields at its entrance and exit apertures~\cite{kim_rf_1989}.

@@

The two main effects contributing to the transverse lens of a $\text{TM}_{010}$-mode RF cavity, its magnetic field component and electric fringe field aperture effects, may also be included within the linear force approximation.
The azimuthal magnetic component of the resonant mode oscillates 90$^{\circ}$ out of phase with the electric component and with a $\operatorname{ J_{1} }$ Bessel radial form; i.e., $ \operatorname{ J_{1} }( k r / a ) \sim k r / a $ for small $r$.
Symmetry and Gauss' Law dictate that in the vicinity of the axial center of the entrance and exit apertures of the RF cavity there exists a radial component of the oscillating electric field determined by $ E_{r} = -\left ( r / 2 \right ) \left ( \partial E_{z} / \partial z \right )_{r=0} $~\cite{kim_rf_1989}, where the form of the axial electric field for $\text{TM}_{010}$ oscillation (\ref{eq:RF_Efield}) implies that, in the context of this analysis, its axial gradient is solely dependent upon the envelope function for the RF cavity (\ref{eq:reg_of_influence}).
In practice, of course, the exact form of $E_{r}(z)$ is strongly tied to the size and shape of the RF cavity apertures (see for example $1 \frac{1}{2}$-cell RF photo-gun designs~\cite{mcdonald_design_1988}). 
For the case of an evacuated cavity, these two contributions result in a net force,
\begin{equation} \label{eq:RF_Force_r}
  \boldsymbol{F}_{ r , RF } = e E_{0} \left [ 
    \frac{ v_{\smallzero} \Omega }{c^{2}} \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) + \frac{2 n}{d} \left ( \frac{z^{\prime} - z^{\prime}_{RF}}{d / 2} \right )^{2 n - 1} \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right )
   \right ] r \hat{\operatorname{ \boldsymbol{r} }} \text{.}
\end{equation}
In obtaining \ref{eq:RF_Force_r}, which is also of the form for use in \ref{eq:linear_force}, we have again used an arbitrary super-Gaussian of order $n$ as a region of influence envelope (see \ref{eq:reg_of_influence}) with $L_{RF} \equiv d$, the RF cavity length.
As will be seen in Section \ref{sec:rf_cav_charge}, under the pulse compression conditions ($\phi = 0$ when the pulse is at $z^{\prime} = 0$), both effects are defocusing for the electron pulse and the magnetic contribution is generally smaller than the transverse lenses associated with the RF cavity apertures when $ d = \pi v_{\smallzero} / \Omega $~\cite{kim_rf_1989}, even though its magnitude is maximized for $\phi = 0$.
Other effects, such as magnetic fringe field aperture effects, could also be included, but are significantly weaker.

### 2013-04-11 inc/extension/initial_conditions/initial_conditions.tex
killing more TODOs
citations are now preceeded by non-breaking space (~)

\section{Determining Appropriate Initial Conditions} \label{sec:initial_conditions}
For a DTEM or UED apparatus, where the electron pulse is produced in a laser-driven photo-electron gun, the implementation of the AG model of Michalik and Sipe \cite{michalik_analytic_2006} requires knowledge of the initial ($ t = 0 $) bunch parameters immediately after generation at the photocathode surface inside the acceleration region of the gun.
For the purposes of this thesis, we will make a simple approximation to the behavior of the gun in order to provide generic initial conditions for the electron pulse.

@@

The initial tranverse properties of the emitted electron beam are easily understood.
The electron pulse's initial spatial variance is simply
\begin{equation}
\sigma_{\smallT } ( 0 ) = ( \Delta x )^{2} = ( \Delta y)^{2} = \frac{ w^{2} }{ 2 } \punct{.}
\end{equation}
For spatially-uniform photoemission from a planar photocathode, from symmetry we have $ \gamma_{\smallT} ( 0 ) = 0 $; i.e., there is no initial transverse spatial momentum chirp across the electron bunch.
Finally, thanks to the careful analysis of Dowell and Schmerge \cite{dowell_quantum_2009} (confirmed by Jensen \textit{et. al.} \cite{jensen_emittance_2010}), we know that metallic photocathode's initial transverse momentum variance at $ t = 0 $ is given by
\begin{equation} \label{eq:jensen_eta}
  \eta_{ \smallT } ( 0 )  = (\Delta p_{\smallT})^2 \approx \frac{ m }{ 3 } ( \hbar \omega - \Phi ) \punct{,}
\end{equation}
in the limit where the maximum excess photoemission energy, $ \Delta E = \hbar \omega - \Phi $ is significantly greater than the thermal energy $ k_{B} T $ of the electrons in the photocathode -- a condition that is generally met in laser-driven DC photoelectron guns.
%TODO include TE value for $\Delta E < 0$  is $\eta_{\smallT} = m k_B T$.

@@

%v0 dominated
In the short pulse limit, where the acceleration in the DC gun field over the incident laser pulse duration can be neglected, the initial electron bunch properties are determined primarily by the photoemission physics.
Since the electric field has no time to influence the front of the pulse before the back is also generated we can say that the front of the pulse has a velocity equal to $v_{max}$ and the back is essentially stationary just after generation.
Further, since the photoemission efficiency is proportional to $\Delta E^2$ \cite{shalaev_electron_1994} the distribution of emitted electrons vs velocity is proportional to $v^4$; therefore to a first approximation it is reasonable to say that in this case $\Delta v \approx v_{max}$.
The pulse's initial spatial variance $\Delta z$ is therefore approximately to the spread of distances traveled during the laser pulse duration $\Delta t_L$,
\begin{equation} 
  \sqrt{ \sigma_{ z } ( 0 ) } \approx \Delta z = \Delta v \Delta t_{L} = \frac{ v_{max} \tau }{ \sqrt{ 2 } } \punct{.}
\end{equation}
Once again, we can use this information to determine a velocity chirp across the pulse in this regime,
\begin{equation}
  \gamma_{ z } ( 0 ) \approx m \Delta v \Delta z = m v_{max} \sqrt{ \sigma_{ z } ( 0 ) } \punct{,}
\end{equation}

@@

We recognize that these initial conditions for an electron pulse generated by a laser-driven DC gun are idealized in that they neglect several important effects; in particular, the interplay of dispersive ($ \eta_{i}(0) \neq 0 $) and space-charge effects in the acceleration region of the photoelectron gun and transverse and longitudinal effects due to the divergence of the DC field in the vicinity of the gun anode \cite{berger_dc_2009,togawa_ceb6_2007}.
Such effects and the limits of the validity of the longitudinal terms of \ref{eq:summary}, within the context of the AG model, will be presented in Section \ref{sec:bin_model}.
However, \ref{eq:summary} also represent a defined set of initial conditions that allows the effect of electron optics (i.e., magnetic lenses and RF cavities) on electron pulse propagation to be more readily understood.
Moreover, they reflect the fact that the majority of DC photoelectron guns are driven by laser pulses with spatial and temporal profiles that are close to Gaussian \cite{williamson_clocking_1997,sciaini_electronic_2009}.
Only for specialized cases, such as the generation of uniform ellipsoid electron bunch shapes, is spatial and temporal manipulation of the incident laser pulse considered \cite{luiten_how_2004,li_generating_2008}.

@@

This limitation on functional form severely limits the accuracy with which a determined spatially constant value of $\eta_z(0)$ represents the actual distribution of momentum uncertainties computed by the binning model.
The self-similar theory of Michalik and Sipe \cite{michalik_analytic_2006} is not equipped to handle such a variation as it assumes a constant $ \eta_{ z } $ over the electron bunch; with a more realistic fit to the simulated initial data, the pulse would eventually evolve to be non-Gaussian.
%Consequently, we will assume that $ \eta_{ z } $ is a constant over the bunch with a value given by $ \eta_{\smallT } ( 0 ) \cong 3.85 \eta{ z } ( 0 ) $: indeed in this short pulse regime, one can show that over the central $ \sim 75 \% $ of the electrons in the inital photo-generated bunch the variation in $ \sqrt{ \eta_{ z } ( 0 ) } $ is only about $ \pm 25 \% $.

>>>>

\section{Determining Appropriate Initial Conditions} \label{sec:initial_conditions}
For a DTEM or UED apparatus, where the electron pulse is produced in a laser-driven photo-electron gun, the implementation of the AG model of Michalik and Sipe~\cite{michalik_analytic_2006} requires knowledge of the initial ($ t = 0 $) bunch parameters immediately after generation at the photocathode surface inside the acceleration region of the gun.
For the purposes of this thesis, we will make a simple approximation to the behavior of the gun in order to provide generic initial conditions for the electron pulse.

@@

The initial tranverse properties of the emitted electron beam are easily understood.
The electron pulse's initial spatial variance is simply
\begin{equation}
\sigma_{\smallT } ( 0 ) = ( \Delta x )^{2} = ( \Delta y)^{2} = \frac{ w^{2} }{ 2 } \punct{.}
\end{equation}
For spatially-uniform photoemission from a planar photocathode, from symmetry we have $ \gamma_{\smallT} ( 0 ) = 0 $; i.e., there is no initial transverse spatial momentum chirp across the electron bunch.
Finally, thanks to the careful analysis of Dowell and Schmerge~\cite{dowell_quantum_2009} (confirmed by Jensen \textit{et. al.}~\cite{jensen_emittance_2010}), we know that metallic photocathode's initial transverse momentum variance at $ t = 0 $ is given by
\begin{equation} \label{eq:jensen_eta}
  \eta_{ \smallT } ( 0 )  = (\Delta p_{\smallT})^2 \approx \frac{ m }{ 3 } ( \hbar \omega - \Phi ) \punct{,}
\end{equation}
in the limit where the maximum excess photoemission energy, $ \Delta E = \hbar \omega - \Phi $ is significantly greater than the thermal energy $ k_{B} T $ of the electrons in the photocathode -- a condition that is generally met in laser-driven DC photoelectron guns.
For completeness we note that for thermionic emission $\Delta p_{\smallT} = \sqrt{m k_B T_e}$ where $k_B$ is the Boltzmann constant and $T_e$ is the electron temperature~\cite{dowell_quantum_2009,jensen_emittance_2010}..

@@

%v0 dominated
In the short pulse limit, where the acceleration in the DC gun field over the incident laser pulse duration can be neglected, the initial electron bunch properties are determined primarily by the photoemission physics.
Since the electric field has no time to influence the front of the pulse before the back is also generated we can say that the front of the pulse has a velocity equal to $v_{max}$ and the back is essentially stationary just after generation.
Further, since the photoemission efficiency is proportional to $\Delta E^2$~\cite{shalaev_electron_1994} the distribution of emitted electrons vs velocity is proportional to $v^4$; therefore to a first approximation it is reasonable to say that in this case $\Delta v \approx v_{max}$.
The pulse's initial spatial variance $\Delta z$ is therefore approximately to the spread of distances traveled during the laser pulse duration $\Delta t_L$,
\begin{equation} 
  \sqrt{ \sigma_{ z } ( 0 ) } \approx \Delta z = \Delta v \Delta t_{L} = \frac{ v_{max} \tau }{ \sqrt{ 2 } } \punct{.}
\end{equation}
Once again, we can use this information to determine a velocity chirp across the pulse in this regime,
\begin{equation}
  \gamma_{ z } ( 0 ) \approx m \Delta v \Delta z = m v_{max} \sqrt{ \sigma_{ z } ( 0 ) } \punct{,}
\end{equation}

@@

We recognize that these initial conditions for an electron pulse generated by a laser-driven DC gun are idealized in that they neglect several important effects; in particular, the interplay of dispersive ($ \eta_{i}(0) \neq 0 $) and space-charge effects in the acceleration region of the photoelectron gun and transverse and longitudinal effects due to the divergence of the DC field in the vicinity of the gun anode~\cite{berger_dc_2009,togawa_ceb6_2007}.
Such effects and the limits of the validity of the longitudinal terms of \ref{eq:summary}, within the context of the AG model, will be presented in Section \ref{sec:bin_model}.
However, \ref{eq:summary} also represent a defined set of initial conditions that allows the effect of electron optics (i.e., magnetic lenses and RF cavities) on electron pulse propagation to be more readily understood.
Moreover, they reflect the fact that the majority of DC photoelectron guns are driven by laser pulses with spatial and temporal profiles that are close to Gaussian~\cite{williamson_clocking_1997,sciaini_electronic_2009}.
Only for specialized cases, such as the generation of uniform ellipsoid electron bunch shapes, is spatial and temporal manipulation of the incident laser pulse considered~\cite{luiten_how_2004,li_generating_2008}.

@@

This limitation on functional form severely limits the accuracy with which a determined spatially constant value of $\eta_z(0)$ represents the actual distribution of momentum uncertainties computed by the binning model.
The self-similar theory of Michalik and Sipe~\cite{michalik_analytic_2006} is not equipped to handle such a variation as it assumes a constant $ \eta_{ z } $ over the electron bunch; with a more realistic fit to the simulated initial data, the pulse would eventually evolve to be non-Gaussian.

### 2013-04-11 inc/extension/liouvilles_theorem/liouvilles_theorem.tex
more punctuation near equations and some equation source reformmatting
citations are now preceeded by non-breaking space (~)

In fact it is easy to show that the AG model explicitly obeys the Liouville Theorem.
To do so, consider the time derivative of these component phase-space products.
Using \ref{eq:ag_original} it is easy to show that
\begin{equation}
  \frac{d}{dt} (\sigma_{\alpha} \eta_{\alpha}) = \sigma_{\alpha} \frac{d \eta_{\alpha}}{dt} + \eta_{\alpha} \frac{d \sigma_{\alpha}}{dt} = 0
\end{equation}
and therefore we can define the per-simulation constants $\Gamma_{\alpha}$ as
\begin{equation} \label{eq:define_big_gamma}
  \Gamma_{\alpha}^2 \equiv \sigma_{\alpha} \eta_{\alpha} = \text{Constant .}
\end{equation}

@@

We note that, in the transverse directions ($\smallT$), this is consistent with the definition of `coherent fluence' employed by Reed \textit{et al.} \cite{reed_evolution_2009} for time-resolved electron microscopy and, of course, the trasverse spatial emittance of an electron beam \cite{jensen_theoretical_2006,siwick_ultrafast_2002}.
Additionally, though the AG model explicitly satisfies Liouville's Theorem, there are cases where the pulse's phase space product may change in a realistic system.
This effect is called ``emittance growth'' and is most commonly seen in TEM as a result of aberations in lens systems \cite{oshea_reversible_1998}.
As will be seen in Section \ref{extension_limitations}, the AG model will, of necessity, only consider perfect lenses.

>>>>

In fact it is easy to show that the AG model explicitly obeys the Liouville Theorem.
To do so, consider the time derivative of these component phase-space products.
Using \ref{eq:ag_original} it is easy to show that
\begin{equation}
  \frac{d}{dt} (\sigma_{\alpha} \eta_{\alpha}) = \sigma_{\alpha} \frac{d \eta_{\alpha}}{dt} + \eta_{\alpha} \frac{d \sigma_{\alpha}}{dt} = 0 \,\text{,}
\end{equation}
and therefore we can define the per-simulation constants $\Gamma_{\alpha}$ as
\begin{equation} \label{eq:define_big_gamma}
  \Gamma_{\alpha}^2 \equiv \sigma_{\alpha} \eta_{\alpha} = \text{Constant .}
\end{equation}

@@

We note that, in the transverse directions ($\smallT$), this is consistent with the definition of `coherent fluence' employed by Reed \textit{et al.}~\cite{reed_evolution_2009} for time-resolved electron microscopy and, of course, the trasverse spatial emittance of an electron beam~\cite{jensen_theoretical_2006,siwick_ultrafast_2002}.
Additionally, though the AG model explicitly satisfies Liouville's Theorem, there are cases where the pulse's phase space product may change in a realistic system.
This effect is called ``emittance growth'' and is most commonly seen in TEM as a result of aberations in lens systems~\cite{oshea_reversible_1998}.
As will be seen in Section \ref{extension_limitations}, the AG model will, of necessity, only consider perfect lenses.

### 2013-04-11 inc/gun/gun_design.tex
citations are now preceeded by non-breaking space (~)

These requirements led to the fabrication of cathode/Wehnelt and anode pair based on the design of Togawa \textit{et al.} \cite{togawa_ceb6_2007} (pictured in \ref{fig:togawa-pic}).
A schematic of this design, overlayed by a Finite Element Model (FEM) simulation of the electic field, is shown in \ref{fig:gun-field}.
The simulation was performed using \texttt{FreeFEM++}, a free finite element partial differential equation solver and meshing toolkit (\url{http://www.freefem.org/ff++/index.htm}).
The FEM simulation modeled the features of the anode and cathode, while emulating gap walls at infinity by placing a linear potential on gap edges at a large distance.
From the field equipotentials, it is clear that this design has a consistently flat electric field for large displacements off the central axis.
Since the shape of the field is scale independent, the schematic shows that the aperture width and laser acceptance concerns are easily satisfied for an appropriate choice of scale.

>>>>

These requirements led to the fabrication of cathode/Wehnelt and anode pair based on the design of Togawa \textit{et al.}~\cite{togawa_ceb6_2007} (pictured in \ref{fig:togawa-pic}).
A schematic of this design, overlayed by a Finite Element Model (FEM) simulation of the electic field, is shown in \ref{fig:gun-field}.
The simulation was performed using \texttt{FreeFEM++}, a free finite element partial differential equation solver and meshing toolkit (\url{http://www.freefem.org/ff++/index.htm}).
The FEM simulation modeled the features of the anode and cathode, while emulating gap walls at infinity by placing a linear potential on gap edges at a large distance.
From the field equipotentials, it is clear that this design has a consistently flat electric field for large displacements off the central axis.
Since the shape of the field is scale independent, the schematic shows that the aperture width and laser acceptance concerns are easily satisfied for an appropriate choice of scale.
